---
title: "pins and Azure from a server"
output: github_document
---

<https://bit.ly/dsi-pin-azure>

## Objectives

See headings outline.



## Use the pins package and register our Azure board

* Use the pins package with `library(pins)`.
* Register our Azure board with `board_register_azure()`

```{r}
library(pins)
board_register_azure()
```



## Find datasets in our Azure board

* Find pins on our Azure board from the Connections tab.
* Find pins on our Azure board with the Addin "Find pins".
* Find pins on our Azure board `pin_find()`, by name or description.

```{r}
pin_find("mt", board = "azure")
```



## Get a dataset from our Azure board

* Get the `mtcars` dataset from our Azure board with `pin_get()`.
* Assign the result to the object `mydata`.
* Inspect mydata however you like. How many rows does it have?

```{r}
mydata <- pin_get("mtcars", board = "azure")
mydata
```



## Save processed data to the server's cache

* Get the `head()` of `mydata` and assign it to a new object `smalldata`.

```{r}
smalldata <- head(mydata)
smalldata
```

* Store `smalldata` in you local (server) cache with `pin()`

```{r}
pin(smalldata)
```

* Find "smalldata" in your local (server) cache, however you like.

```{r}
pin_find("smalldata")
```

* Get "smalldata" from your local (server) cache.

```{r}
pin_get("smalldata", board = "local")
```



## Visualize the structure of the server's cache.

* Create a path to the local (server) cache that pins created for you.

```{r}
server_cache <- board_cache_path()
server_cache
```

* Explore the structure of the local (server) cache with fs::dir_tree().

```{r}
fs::dir_tree(server_cache)
```



## Takeaways

* Go to the collaborative document and write your takeaways.

<bit.ly/dsi-pin-azure>
