---
title: "Creating and using timestamped pins"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  cache = FALSE,
  comment = "#>",
  collapse = TRUE
)
```

This lesson shows workflows that seem common for data admins and data analysts working in a team. It shows how to programatically add timestamped versions of a dataset to an Azure board for pins, and how to programatically get the latest version. This is how I imagine we could work at 2Dii, but please do let me know if this won't work, why, and hopefully an idea about how we may adapt it to fit your needs.

## Setup

* Setup your environmental variables: 01_setup-azure-board.Rmd.
* Use pins and register the Azure board (expect no output).

```{r}
library(pins)
board_register_azure()
```

## A data admin creates a timestamped pin.

Here I'm setting the few parameters that vary: the dataset itself and the dataset name.

```{r}
x <- mtcars
name <- "a_dataset"
description <- "A flat file from the database"
```

We now create a new timestamped name and use it to create a new pin of the the dataset we want to share.

```{r}
# Helper
timestamp_name <- function(name) {
  timestamp <- format(Sys.time(), "%F_%H-%M-%S")
  paste0(name, "_", timestamp)
}

(name_now <- timestamp_name(name))

pin(x, name = name_now, board = "azure", description = description)
```

Let's see the last few timestamped versions we have on the Azure board. I use `tail()` because I created many versions and but we only care about the last few.

```{r}
tail(pin_find(name), 2)
```

## Verify the timestamped pins are accumulating 

Let's confirm that
(name_now <- timestamp_name(name)I create a new timestamped version of the)
dataset every time I call `pin(name_now, board = "azure")`. To make this clearer I first wait for a few seconds so the timestamps are different by more than one second. I then pin yet another timestamped version of the working dataset.

```{r}
Sys.sleep(3)
(name_now <- timestamp_name(name))

pin(x, name = name_now, board = "azure", description = description)
```

And again I explore the last few timestamped versions I now have on the Azure board.

```{r}
tail(pin_find(name), 2)
```

## An analyst gets the latest timestamped dataset

An analyst may get any timestamped version; commonly the latest one.

```{r}
# See pins setup: 01_setup-azure-board.Rmd
library(pins)
board_register_azure()

(latest <- dplyr::last(pin_find(name)$name))

pin_get(latest)
```

