---
title: "Creating and using timestamped pins"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  cache = FALSE,
  comment = "#>",
  collapse = TRUE
)
```

This lesson shows workflows that seem common for data admins and data analysts working in a team. It shows how to programatically add timestamped versions of a dataset to an Azure board for pins, and how to programatically get the latest version. This is how I imagine we could work at 2Dii, but please do let me know if this won't work, why, and hopefully an idea about how we may adapt it to fit your needs.

## Setup

* Setup your environmental variables: 01_setup-azure-board.Rmd.
* Use pins and register the Azure board (expect no output).

```{r}
library(pins)
board_register_azure()
```

## A data admin creates a timestamped pin.

Setup the two things that vary: the dataset itself and the dataset name.

```{r}
x <- mtcars
name <- "a_dataset"
description <- "A flat file from the database"
```

* Helper to create a timestamped file name.

```{r}
# Helper
timestamp_name <- function(filename) {
  timestamp <- format(Sys.time(), "%F_%H-%M")
  paste0(filename, "_", timestamp)
}
```

* Pin a new timestamped version of the working dataset.

```{r}
(name_now <- timestamp_name(name))
pin(x, name_now, board = "azure", description = description)
```

* Explore available timestamped versions on the Azure board.

```{r}
tail(pin_find(name), 2)
```

## Verify the timestamped pins are accumulating 

Here I repeat to confirm we create a new timestamped file every time we call `pin(timestamp_name(name), board = "azure")`.

* To make this clearer I first wait for a few seconds.

```{r}
Sys.sleep(3)
```
* I now pin a new timestamped version of the working dataset.

```{r}
(name_now <- timestamp_name(name))
pin(x, name_now, board = "azure", description = description)
```

* Again I explore available timestamped versions on the Azure board.

```{r}
tail(pin_find(name), 2)
```

## An analyst gets the latest timestamped dataset

* An analyst may get any timestamped version; commonly the latest one.

```{r}
# See pins setup: 01_setup-azure-board.Rmd
library(pins)
board_register_azure()

(latest <- dplyr::last(pin_find(name)$name))

pin_get(latest)
```

