---
title: "pins and Azure from a server"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  cache = FALSE,
  comment = "#>",
  collapse = TRUE
)
```

This lesson is mostly for data admins. The goal is to add new timestamped versions of a dataset to an Azure board for pins.

## Setup

* Setup your environmental variables: 01_setup-azure-board.Rmd.
* Use pins and register the Azure board (expect no output).

```{r}
library(pins)
board_register_azure()
```

## A data admin creates a timestamped pin.

Setup the two things that vary: the dataset itself and the dataset name.

```{r}
x <- mtcars
name <- "a_dataset"
description <- "A flat file from the database"
```

* Helper to create a timestamped file name.

```{r}
# Helper
timestamp_name <- function(filename) {
  timestamp <- format(Sys.time(), "%F_%H-%M")
  paste0(filename, "_", timestamp)
}
```

* Pin a new timestamped version of the working dataset.

```{r}
(name_now <- timestamp_name(name))
pin(x, name_now, board = "azure", description = description)
```

* Explore available timestamped versions on the Azure board.

```{r}
tail(pin_find(name), 2)
```

## Verify the timestamped pins are accumulating 

Here I repeat to confirm we create a new timestamped file every time we call `pin(timestamp_name(name), board = "azure")`.

* To make this clearer I first wait for a few seconds.

```{r}
Sys.sleep(3)
```
* I now pin a new timestamped version of the working dataset.

```{r}
(name_now <- timestamp_name(name))
pin(x, name_now, board = "azure", description = description)
```

* Again I explore available timestamped versions on the Azure board.

```{r}
tail(pin_find(name), 2)
```

## An analyst gets the latest timestamped dataset

* An analyst may get any timestamped version; commonly the latest one.

```{r}
# See pins setup: 01_setup-azure-board.Rmd
library(pins)
board_register_azure()

(latest <- dplyr::last(pin_find(name)$name))

pin_get(latest)
```

